---
title: "Biol 432 Assignment 3"
author: "Chenyang Wu"
date: "2022/1/26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Project Info
#### **GitHub user name**: Wuris
#### **Date**: 2022/1/26
#### **GitHub Link**: https://github.com/Wuris/Biol432_Assignment3.git

### Load the FallopiaData.csv
```{r}
setwd("E:/Underguaduate/4th Fourth year/BIOL 432/Week 3/Biol432_Assignment3")
A3Data <- read.csv("InputData/FallopiaData.csv")
```

### Load some packages
```{r}
library(dplyr)
```

### Remove rows with ‘Total’ biomass < 60
```{r}
A3Data_New <- A3Data %>%
  filter(Total < 60)
```

### Reorder the columns so that they are in the order: ‘Total’, ‘Taxon’, ‘Scenario’, ‘Nutrients’, and remove the other columns
```{r}
A3Data_New <- A3Data_New %>% 
  select(Total, Taxon, Scenario, Nutrients)
```

### Make a new column TotalG, which converts the ‘Total’ column from mg to grams AND replace Total with TotalG, and add it to the dataset.
```{r}
A3Data_New$TotalG = A3Data_New$Total*0.001

A3Data_New <- A3Data_New %>% 
  select(TotalG, Taxon, Scenario, Nutrients)
```

### Write a custom function that will take two inputs from the user: 1. a vector of data to process (e.g. column from a data.frame object) and 2. a string that defines what calculation to perform.
#### if string #2 is "Average" then calculate the average value for the column named in vector #1
#### if string #2 is "Sum" then calculate the sum of values for the column named in vector #1
#### if string #2 is "Observations" then count the number of observed values for the column named in vector #1
#### if string #2 is anything else, then output an error to the user 
```{r}
my_custom_function <- function(x, y){
  if(y == "Average"){
    return(mean(x))
  } else if(y == "Sum"){
    return(sum(x))
  } else if(y == "Observations"){
    return(length(x))
  } else {
    return(print("Error!"))
  }
}
```

### Write some R code that uses your function to count the total number of observations in the 'Taxon' column.
```{r}
my_custom_function(A3Data_New$Taxon, "Observations")
```

### Write some R code that uses your function to calculate the average TotalG for each of the two Nutrient concentrations.
```{r}
A3Data_New %>% 
  group_by(Nutrients) %>% 
  summarise(Average = my_custom_function(TotalG, "Average"))
```

### Write (i.e. save) the new data to a file called "WrangledData.csv" in the Output folder. 
```{r}
write.csv(A3Data_New, "./Output/WrangledData.csv") 
```

### Test your script for errors
```{r}
Test <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)

my_custom_function(Test, "Average")

my_custom_function(Test, "Sum")

my_custom_function(Test, "Observations")

my_custom_function(Test, "Anything else, for error")

```

